Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-19 latex/article.tex
intro minor edits

\graphicspath{{./Figs/}}
\input{macros}
\begin{document}
\maketitle

\begin{abstract}\sloppy
  Interactive visualization is a very convenient tool to explore
  complex scientific data or to explore different parameter settings
  for a given processing algorithm. In this article, we present a tool
  to efficiently explore the curvature tensor on the boundary of
  potentially large digital objects. More precisely, we combine a
  fully parallel pipeline on GPU to extract an adaptive triangulated
  isosurface of the digital object, with a curvature tensor
  estimation at each surface point based on integral
  invariants. Integral invariants being parametrized by a given ball
  radius, our proposal allows us to explore interactively different
  radii and thus select the appropriate scale to which the computation
  is performed and visualized. Mean and gaussian curvature, principal
  curvatures, principal directions and normal vector field may be interactively
  visualized with our technique.

>>>>

\graphicspath{{./figs/}}
\input{macros}
\begin{document}
\maketitle

\begin{abstract}\sloppy
  Interactive visualization is a very convenient tool to explore
  complex scientific data or to explore different parameter settings
  for a given processing algorithm. In this article, we present a tool
  to efficiently explore the curvature tensor on the boundary of
  potentially large and dynamic digital objects (mean and gaussian curvature,
  principal curvatures, principal directions and normal vector
  field). More precisely, we combine a fully parallel pipeline on GPU
  to extract an adaptive triangulated isosurface of the digital
  object, with a curvature tensor estimation at each surface point
  based on integral invariants. Integral invariants being parametrized
  by a given ball radius, our proposal allows us to explore
  interactively different radii and thus select the appropriate scale
  to which the computation is performed and visualized.
